\documentclass{book}
\usepackage{sstdef}
\title{shttpd}
\begin{document}
\section{shttpd}

\begin{chapterintro}
\href{How to install shttpd}{install.html}\\
\href{How to upgrade shttpd}{upgrade.html}\\

\href{The \cmd{echo-httpd} program}{echo-httpd.html}\\
\href{The \cmd{echo-config} program}{echo-config.html}\\

\href{The \cmd{redir-httpd} program}{redir-httpd.html}\\
\href{The \cmd{redir-config} program}{redir-config.html}\\
\href{The \cmd{redir-data} program}{redir-data.html}\\

\href{The \cmd{cgi-httpd} program}{cgi-httpd.html}\\
\href{The \cmd{cgi-config} program}{cgi-config.html}\\

\href{The \cmd{cgiuser-httpd} program}{cgiuser-httpd.html}\\
\href{The \cmd{cgiuser-config} program}{cgiuser-config.html}\\

\href{The \cmd{cgi-dispatch} program}{cgi-dispatch.html}\\

\href{The \cmd{constant-httpd} program}{constant-httpd.html}\\
\href{The \cmd{constant-config} program}{constant-config.html}\\

\href{A mailing list for shttpd discussion}{../lists.html\#shttpd}\\
\end{chapterintro}

\subsection{What is shttpd?}
\cmd{echo-httpd}, \cmd{redir-httpd}, and \cmd{cgi-httpd} are HTTP
daemons designed to complement publicfile.

\cmd{echo-httpd} echos HTTP requests.

\cmd{echo-config} configures \cmd{echo-httpd}.

\cmd{redir-httpd} redirects HTTP requests via cdb lookup.

\cmd{redir-config} configures \cmd{redir-httpd}.

\cmd{cgi-httpd} and \cmd{cgiuser-httpd} execute a cgi script.

\cmd{cgi-config} and \cmd{cgiuser-config} configure \cmd{cgi-httpd} and
\cmd{cgiuser-httpd}, respectively.

\cmd{cgi-dispatch} executes a CGI program specified by the environment variable
\cmd{PATH_INFO}.

\cmd{constant-httpd} prints the same file for each HTTP request.

\cmd{constant-config} configures \cmd{constant-httpd}.

Each instance of an shttpd daemon listens on a separate address, in a
\cmd{chroot} directory (except for \cmd{cgiuser-httpd}), typically running as a
nonprivileged user.

\subsection{Related Software}
The shttpd package complements \href{publicfile}{http://cr.yp.to/publicfile.html}.
\end{document}
